An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-16 EconGrowth-R-Functions.Rnw
In the process of building 9-panel graphs for CI vs. param plots.

# Statistical significance levels. We'll work with 95% CIs
ciLevel <- 0.95
ciHalfLevel <- ciLevel + (1.0-ciLevel)/2.0
# List of countries
countryAbbrevs <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
countryAbbrevsAlph <- c(CN="CN", IR="IR", JP="JP", SA="SA", TZ="TZ", UK="UK", US="US", ZA="ZA", ZM="ZM")
countryAbbrevsU <- c(US="US", UK="UK", JP="JP") #Only these countries have useful work data
countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
yLimitsForGDPGraphs <- list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)) # Alph order
energyTypes <- c(Q="Q", X="X", U="U") # List of energy types
factors <- c(K="K", L="L", Q="Q", X="X", U="U") # List of factors of production
########### Several global parameters for graphs. Set here and use below to ensure consistent appearance of graphs.
# Set the order for presenting countries in 3x3 lattice graphs. Default is alphabetical. 
# "1" means first alphabetically.
countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9) # Sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
timeTics <- c(1980, 1990, 2000, 2010)
yTicsForIndexedGraphs <- c(1,2,3,4,5,6,7,8,9,10) #y tic mark locations.

@@

@@

@@

@@

@@

    x <- subset(data, select=m) # The column of ms

@@

@@

@@

@@

@@

@@

@@

@@

    x <- subset(data, select=delta_1) # The column of delta_1

@@

@@

    x <- subset(data, select=sigma_1) # The column of sigma_1

@@

@@

    x <- subset(data, select=delta) # The column of delta

@@

@@

    x <- subset(data, select=sigma) # The column of sigma

@@

@@

    x <- subset(data, select=a_0) # The column of a_0s

@@

@@

    x <- subset(data, select=c_t) # The column of c_ts

@@

@@

@@

  data <- cbind(x, y)
  plot <- xyplot(data[ , 2] ~ data[ , 1], # data[ , 1] contains the the parameter; data[ , 2] contains the CIs

>>>>

# Statistical significance levels. We'll work with 95% CIs
ciLevel <- 0.95
ciHalfLevel <- ciLevel + (1.0-ciLevel)/2.0
# List of countries
countryAbbrevs <- c(US="US", UK="UK", JP="JP", CN="CN", ZA="ZA", SA="SA", IR="IR", TZ="TZ", ZM="ZM")
countryAbbrevsAlph <- c(CN="CN", IR="IR", JP="JP", SA="SA", TZ="TZ", UK="UK", US="US", ZA="ZA", ZM="ZM")
countryAbbrevsU <- c(US="US", UK="UK", JP="JP") #Only these countries have useful work data
countryAbbrevsAlphU <- c(JP="JP", UK="UK", US="US")
countryNamesAlph <- c(CN="China", IR="Iran", JP="Japan", SA="Saudi Arabia", TZ="Tanzania", UK="United Kingdom", US="USA", ZA="South Africa", ZM="Zambia") #In alphabetical order.
yLimitsForGDPGraphs <- list(c(1,10), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4), c(1,4)) # Alph order
energyTypes <- c(Q="Q", X="X", U="U") # List of energy types
factors <- c(K="K", L="L", Q="Q", X="X", U="U") # List of factors of production
########### Several global parameters for graphs. Set here and use below to ensure consistent appearance of graphs.
# Set the order for presenting countries in 3x3 lattice graphs. Default is alphabetical. 
# "1" means first alphabetically.
countryOrderForGraphs <- c(7,6,3,1,8,5,4,2,9) # Sets the order as US, UK, JP, CN, ZA, TZ, SA, IR, ZM.
timeTics <- c(1980, 1990, 2000, 2010)
yTicsForIndexedGraphs <- c(1,2,3,4,5,6,7,8,9,10) #y tic mark locations.

@@

############################
# Creates a data.frame that contains the following information:
# row name: 2-letter country abbreviation
# 1st col: parameter value. The name of this column is the name of the parameter, "sigma", "delta", etc. 
#          as appropriate for the model generating the data
# 2nd col: width of the confidence interval. The name of this column is "CI"
# 3rd col: an identifier for parameter, model, and (factor or energy type). 
#          For example, if you want the sigma parameter for the CES model with Q, you would get "sigmaCESeq".
#          If you want the m parameter for the single-factor mdoel with k, you would get "mSFk".
#          If you want the alpha parameter for the Cobb-Douglas model without energy, you would get "alphaCD".
#          The name of the column is "factor"
CIvsParamDF <- function(model, param, energyType=NA, factor=NA){
    x <- subset(data, select=m) # The column of m's
    x <- subset(data, select=delta_1) # The column of delta_1's
    x <- subset(data, select=sigma_1) # The column of sigma_1's
    x <- subset(data, select=delta) # The column of deltas
    x <- subset(data, select=sigma) # The column of sigmas
    x <- subset(data, select=a_0) # The column of a_0's
    x <- subset(data, select=c_t) # The column of c_t's
  # Create the factor string. We are guaranteed to have a value for the param and model arguments.
  # However, we might have NA for either energyType or factor. But, we will not have values for both 
  # energyType and factor at the same time! So, we can simply paste everything together here and 
  # obtain the desired result.
  if (is.na(factor)){
    factorString <- paste(param, model, energyType, sep="")
  } else if (is.na(energyType)){
    factorString <- paste(param, model, factor, sep="")
    print("Neither energyType nor factor were NA in CIvsParamDF. But one should be.")
    return(NULL)
  nRows <- nrow(x)
  factor <- as.data.frame(matrix(factorString, ncol=1, nrow=nRows))
  colnames(factor) <- "factor"
  data <- cbind(x, y, factor)
  return(data)

@@

  data <- CIvsParamDF(model=model, param=param, energyType=energyType, factor=factor)
#   if (model == "SF"){data <- singleFactorParamsDF(factor)} 
#   else if (model == "CD"){data <- cobbDouglasParamsTableNoEnergyDF()}
#   else if (model == "CDe"){data <- cobbDouglasParamsTableWithEnergyDF(energyType)}
#   else if (model == "CES"){data <- cesParamsTableDF(energyType=NA)}
#   else if (model == "CESe"){data <- cesParamsTableDF(energyType)}
#   else if (model == "LINEX"){data <- linexParamsTableDF(energyType)}
#   # Now get the data for the parameter requested

@@

#     x <- subset(data, select=lambda) # The column of lambdas

@@

#     y <- subset(data, select=upperCI_lambda) - subset(data, select=lowerCI_lambda) # A column of CI values

@@

#     x <- subset(data, select=m) # The column of ms
#     colnames(x) <- "m"

@@

#     y <- subset(data, select=upperCI_m) - subset(data, select=lowerCI_m) # A column of CI values

@@

#     x <- subset(data, select=alpha) # The column of alphas

@@

#     y <- subset(data, select=upperCI_alpha) - subset(data, select=lowerCI_alpha) # A column of CI values

@@

#     x <- subset(data, select=beta) # The column of betas

@@

#     y <- subset(data, select=upperCI_beta) - subset(data, select=lowerCI_beta) # A column of CI values

@@

#     x <- subset(data, select=gamma) # The column of gammas

@@

#     y <- subset(data, select=upperCI_gamma) - subset(data, select=lowerCI_gamma) # A column of CI values

@@

#     x <- subset(data, select=delta_1) # The column of delta_1

@@

#     y <- subset(data, select=upperCI_delta_1) - subset(data, select=lowerCI_delta_1) # A column of CI values

@@

#     x <- subset(data, select=sigma_1) # The column of sigma_1

@@

#     y <- subset(data, select=upperCI_sigma_1) - subset(data, select=lowerCI_sigma_1) # A column of CI values

@@

#     x <- subset(data, select=delta) # The column of delta

@@

#     y <- subset(data, select=upperCI_delta) - subset(data, select=lowerCI_delta) # A column of CI values

@@

#     x <- subset(data, select=sigma) # The column of sigma

@@

#     y <- subset(data, select=upperCI_sigma) - subset(data, select=lowerCI_sigma) # A column of CI values

@@

#     x <- subset(data, select=a_0) # The column of a_0s

@@

#     y <- subset(data, select=upperCI_a_0) - subset(data, select=lowerCI_a_0) # A column of CI values

@@

#     x <- subset(data, select=c_t) # The column of c_ts

@@

#     y <- subset(data, select=upperCI_c_t) - subset(data, select=lowerCI_c_t) # A column of CI values

@@

#   colnames(y) <- "CI"

@@

#   data <- cbind(x, y)
  # Need to use the indices in the following code, because the column labels will be different for each type
  # of model. In other words, if we're doing CESe with Q and plotting sigma, the data.frame will come 
  # back with column names of "sigma" and "CI" on the first and second column, respectively. 
  # plot <-  xyplot(data$CI ~ data$sigma, ...)
  # would break if we, instead, wanted CESe with Q and plotting delta.
  # So, instead, we use the column indices to pick off the correct variables.
  plot <- xyplot(data[ , 2] ~ data[ , 1], # data[ , 1] contains the the parameter; data[ , 2] contains the CI width

### 2013-04-16 EconGrowth.Rnw
In the process of building 9-panel graphs for CI vs. param plots.

@@

@@

<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", fig.pos="H", eval=TRUE>>=
cdeGridLattice(energyType="Q")
@

>>>>

\item{Heun: Eliminate non-developed countries from partial residual plots.}

@@

<<Test, eval=TRUE>>=
CIvsParamDF(model="CESe", param="sigma", energyType="Q")
CIvsParamPlot(model="CESe", param="sigma", energyType="Q")

@

@@

<<CDeGridLattice, fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Grid search over $\\gamma$ for Cobb-Douglas with energy model.", fig.pos="H">>=
cdeGridLattice(energyType="Q")
@

### 2013-04-16 EconGrowthSeminar.Rnw
In the process of building 9-panel graphs for CI vs. param plots.

\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph(countryAbbrev="JP", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{JP}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph(countryAbbrev="CN", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{CN}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph(countryAbbrev="ZA", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{ZA}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph(countryAbbrev="SA", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{SA}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph(countryAbbrev="IR", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{IR}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph(countryAbbrev="TZ", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{TZ}{0.07}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridGraph(countryAbbrev="ZM", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{ZM}{0.055}
\end{frame}

>>>>

\begin{frame}{Grid Search Over $\gamma$}{JP Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsJP, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridLattice(countryAbbrev="JP", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{JP}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{CN Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsCN, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridLattice(countryAbbrev="CN", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{CN}{0.045}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{ZA Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsZA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridLattice(countryAbbrev="ZA", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{ZA}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{SA Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsSA, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridLattice(countryAbbrev="SA", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{SA}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{IR Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsIR, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridLattice(countryAbbrev="IR", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{IR}{0.055}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{TZ Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsTZ, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridLattice(countryAbbrev="TZ", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{TZ}{0.07}
\end{frame}

\begin{frame}{Grid Search Over $\gamma$}{ZM Cobb-Douglas with $q$} %----------------------------
<<CDeGammaGraphsZM, fig.width=presentationGraph1ColWidth, fig.height=presentationGraph1RowHeight>>=
  cdeGridLattice(countryAbbrev="ZM", energyType="Q", textScaling=0.8)
@
  % Including at bottom of frame so as not to push other material downward in the frame.
  \putFlagUpperRight{ZM}{0.055}
\end{frame}
